Automatically proving equivalence by type-safe reflection

### 2016-01-19 paper-JFP-DTP/content/3-generalProblem.tex
corrections with Edwin advices on latex

\section {Back to the general problem : A hierarchy of tactics}

@@

All of our tactics will require to have a way of testing this equivalence between elements of the underlying set, that is to say, a way to test equivalence between constants. For this reason, we define a notion of "set", which only requires the definition of the equivalence relation --accompanied with the proofs that this is indeed an equivalence relation-- and this equivalence test $set\_eq$. All the algebraic structures will later extend this type class :

@@

    set_eq : (x:c) $\rightarrow$ (y:c) $\rightarrow$ Maybe (x $\simeq$ y)
\end{lstlisting}
\end{center}
\caption{Set}
\figrule
\end{figure}
If the user wants to prove propositional equalities, then he will simply instantiate $(\simeq)$ with the built-in $(=)$ during the definition of the instance of $Set$.
Note that $(\simeq)$ is only weakly decidable in the sense that $set\_eq$ only produces a proof when the two elements are equivalent, but it doesn't produce a proof of dis-equivalence when they are different -- instead, it simply produces the value $Nothing$--. That's quite natural, since we want to generate proof of equivalence, and not to generate counter examples for proving dis-equivalence, which is another problem.

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
class Set c => Magma c where
    Plus : c $\rightarrow$ c $\rightarrow$ c
\end{lstlisting}
\end{center}
\caption{Magma}
\figrule
\end{figure}

This code means that a type $c$ (for $carrier$) is a Magma if it is already a Set (ie, it is equiped with the equivalence relation $\simeq$ and the test $set\_eq$), and if it has a $Plus$ operation.
In fact, all operations, like the Plus here, need to be "compatible" with the equality : $Plus\_preserves\_equiv : \{c1:c\} \rightarrow \{c2:c\} \rightarrow \{c1':c\} \rightarrow \{c2':c\} \rightarrow (c1 \simeq c1') \rightarrow (c2 \simeq c2') \rightarrow (Plus\ c1\ c2) \simeq (Plus\ c1'\ c2')$. This need only comes from the fact that we're dealing with any equivalence relation

A bit more interesting is the Semi-Group type class. A semi-Group is a Magma (ie, it still has a $Plus$ operation), but moreover it has the property of associativity for this operation.

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
class Magma c => SemiGroup c where
    Plus_assoc : (c1:c) $\rightarrow$ (c2:c) $\rightarrow$ (c3:c) 
               -> (Plus (Plus c1 c2) c3 $\simeq$ Plus c1 (Plus c2 c3))
\end{lstlisting}
\end{center}
\caption{Semi-Group}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
class SemiGroup c => Monoid c where
    Zero : c    
    Plus_neutral_1 : (c1:c) $\rightarrow$ (Plus Zero c1 $\simeq$ c1)    
    Plus_neutral_2 : (c1:c) $\rightarrow$ (Plus c1 Zero $\simeq$ c1)
\end{lstlisting}
\end{center}
\caption{Monoid}
\figrule
\end{figure}
We can continue the hierarchy with groups, which are a more interesting.
A group is a monoid, with two new operations. The binary operation $Minus$, and the unary operation $Neg$. We must have the property that $Minus$ can always be simplified with the $Neg$ and the $Plus$. That means that $Minus$ is not a "primitive" operation of a Group, since we can always rewrite $(a-b)$ into $(a\ +\ -b)$. We let the possibility to express a $Minus$ just for convenience for the user, as he won't have to rewrite by hand his $Minus$ operations with sums of negations.
The second axiom, which is the most important one for a Group, is the fact that any value $c1$ admits $Neg\ c1$ for inverse, where being an inverse is the following property :

@@

class Monoid c => Group c where
    Minus : c $\rightarrow$ c $\rightarrow$ c
    Neg : c $\rightarrow$ c
    Minus_simpl : (c1:c) $\rightarrow$ (c2:c) $\rightarrow$ Minus c1 c2 $\simeq$ Plus c1 (Neg c2) 
    Plus_inverse : (c1:c) $\rightarrow$ hasSymmetric c _ c1 (Neg c1)
\end{lstlisting}
\end{center}
\caption{Group}
\figrule
\end{figure}

@@

Note that the properties will either be obtained "by implementation" if the operations are real --computable-- functions, or by axioms if the user is working in an axiomatised theory where the operations ($Plus$, $Neg$, ...) are defined as axioms.

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
data ExprMa : Magma c $\rightarrow$ (Vect n c) $\rightarrow$ c $\rightarrow$ Type where
    ConstMa : (p : Magma c) $\rightarrow$ ($\Gamma$:Vect n c) $\rightarrow$ (c1:c)  $\rightarrow$ ExprMa p $\Gamma$ c1 
    PlusMa : {p : Magma c} $\rightarrow$ {$\Gamma$:Vect n c} $\rightarrow$ {c1:c} $\rightarrow$ {c2:c} 
         $\rightarrow$ ExprMa p $\Gamma$ c1 $\rightarrow$ ExprMa p $\Gamma$ c2 
         $\rightarrow$ ExprMa p $\Gamma$ (Plus c1 c2) 
    VarMa : (p:Magma c) $\rightarrow$ {$\Gamma$:Vect n c}
         $\rightarrow$ (i:Fin n) $\rightarrow$ ExprMa p $\Gamma$ (index i $\Gamma$)
\end{lstlisting}
\end{center}
\caption{Reflected terms for a Magma}
\figrule
\end{figure}

@@

%For the moment, the definition of $Variable$ is just the following:
%
%\begin{code}[caption=Reflected variables, captionpos=b, label=lst1:haskell2]  
%data Variable : {c:Type} -> {n:Nat}
%  -> (c_equal : (c1:c)->(c2:c)->Maybe(c1=c2)) 
%  -> (Vect n c) -> c -> Type where
%    RealVariable : (c_equal:(c1:c)->(c2:c)
%                    ->Maybe(c1=c2))
%          -> ($\Gamma$:Vect n c) -> (i:Fin n) 
%          -> Variable c_equal $\Gamma$ (index i $\Gamma$) 
%\end{code}	
%
%This type will be extended with some other constructors later on. For the moment, we can only %express a "real variable", referred by its index $i$. \\
%\\
Because there is no additional operations in a SemiGroup or in a Monoid, the datatypes for reflected terms in these two structures will have exactly the same shape as the one for Magma that we've given above.
However, the one for $Group$ will introduce two new constructors for the $Neg$ and $Minus$ operations :

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
data ExprG :  Group c $\rightarrow$ (Vect n c) $\rightarrow$ c $\rightarrow$ Type where
    ConstG : (p : dataTypes.Group c) $\rightarrow$ ($\Gamma$:Vect n c) 
         -> (c1:c) $\rightarrow$ ExprG p $\Gamma$ c1
    PlusG : {p : Group c} $\rightarrow$ {$\Gamma$:Vect n c} $\rightarrow$ {c1:c} $\rightarrow$ {c2:c} 
         $\rightarrow$ ExprG p $\Gamma$ c1 $\rightarrow$ ExprG p $\Gamma$ c2 
         $\rightarrow$ ExprG p $\Gamma$ (Plus c1 c2)
    MinusG : {p : Group c} $\rightarrow$ {$\Gamma$:Vect n c} $\rightarrow$ {c1:c} $\rightarrow$ {c2:c} 
         $\rightarrow$ ExprG p $\Gamma$ c1 $\rightarrow$ ExprG p $\Gamma$ c2 
         $\rightarrow$ ExprG p $\Gamma$ (Minus c1 c2)
    NegG : {p : Group c} $\rightarrow$ {$\Gamma$:Vect n c} $\rightarrow$ {c1:c} 
         $\rightarrow$ ExprG p $\Gamma$ c1 $\rightarrow$ ExprG p $\Gamma$ (Neg c1)
    VarG : (p : Group c) $\rightarrow$ {$\Gamma$:Vect n c} 
         $\rightarrow$ (i:Fin n) $\rightarrow$ ExprG p $\Gamma$ c1
\end{lstlisting}
\end{center}
\caption{Reflected terms in a Group}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
groupReduce : {c:Type} $\rightarrow$ {n:Nat} $\rightarrow$ (p:Group c) $\rightarrow$ {$\Gamma$:Vect n c} 
	   $\rightarrow$ {x:c} $\rightarrow$ (ExprG p $\Gamma$ x) $\rightarrow$ (x' ** (ExprG p $\Gamma$ x', x $\simeq$ x'))
\end{lstlisting}
\end{center}
\caption{Type of the reduction function for terms reflecting elements in a Group}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
groupDecideEq : (p:Group c) $\rightarrow$ {$\Gamma$:Vect n c} $\rightarrow$ {x : c} $\rightarrow$ {y : c} 
	     $\rightarrow$ (ExprG p $\Gamma$ x) $\rightarrow$ (ExprG p $\Gamma$ y) 
	     $\rightarrow$ Maybe (x $\simeq$ y)
\end{lstlisting}
\end{center}
\caption{Type of the function for deciding equality between elements in a Group}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
groupDecideEq p ex ey =
  let (x' ** (ex', px)) = groupReduce p ex in
  let (y' ** (ey', py)) = groupReduce p ey in
	     buildProofGroup p ex' ey' px py
\end{lstlisting}
\end{center}
\caption{Decides if two elements of a group are equal}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
buildProofGroup : (p:Group c) $\rightarrow$ {$\Gamma$:Vect n c} 
  $\rightarrow$ {x : c} $\rightarrow$ {y : c} $\rightarrow$ {x':c} $\rightarrow$ {y':c} 
  $\rightarrow$ (ExprG p $\Gamma$ x') $\rightarrow$ (ExprG p $\Gamma$ y') 
  $\rightarrow$ (x $\simeq$ x') $\rightarrow$ (y $\simeq$ y') 
  $\rightarrow$ (Maybe (x $\simeq$ y))
buildProofGroup p ex' ey' px py with (exprG_eq p ex' ey')
    buildProofGroup p ex' ex' px py | Just refl = ?MbuildProofGroup
    buildProofGroup p ex' ey' px py | Nothing = Nothing
\end{lstlisting}
\end{center}
\caption{Composes the two proofs if the normal forms are the same}
\figrule
\end{figure}
We've used here the function $exprG\_eq$ to decide the syntactical equality between the normalised reflected terms $ex'$ and $ey'$. This function plays the same role as $eqExpr$, presented on section 2.3 for the smaller example. Also, the proof for the metavariable $MbuildProofGroup$ corresponds exactly to what was done for the metariable $MbuildProof$ in the smaller example.

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
ConstantsRingReflector : {c:Type} $\rightarrow$ (p:Ring c) $\rightarrow$ Type
ConstantsRingReflector {c=c} p = 
     ({n:Nat} $\rightarrow$ ($\Gamma$:Vect n c) $\rightarrow$ (x:c) $\rightarrow$ Maybe (ExprR p $\Gamma$ x))
\end{lstlisting}
\end{center}
\caption{Type of the function doing the reflection for constants}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
reflectRingTerm : {c:Type} $\rightarrow$ {p:Ring c} $\rightarrow$ {n:Nat} $\rightarrow$ ($\Gamma$ : Vect n c) 
     $\rightarrow$ (funReflectCsf:ConstantsRingReflector {c=c} p) $\rightarrow$ (x:c) 
     $\rightarrow$ (n' ** ($\Gamma'$:Vect n' c ** (ExprR {c=c} {n=n+n'} p ($\Gamma$ ++ $\Gamma'$) x)))
\end{lstlisting}
\end{center}
\caption{Automatic reflection to ring}
\figrule
\end{figure}

This function will work very similarly to the reflection function for $Nat$ that we've writen in section 2.5. Here, there are just more constructions to deal with, because $c$ is equipped with negations, subtractions and multiplications. We just show the pattern for the multiplication.

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
reflectRingTerm {p} {n=n} $\Gamma$ funReflectCsf (a*b) = 
   let (n' ** ($\Gamma'$ ** a')) = reflectRingTerm $\Gamma$ funReflectCsf a in
   let (n'' ** ($\Gamma''$ ** b')) = reflectRingTerm ($\Gamma$ ++ $\Gamma'$) funReflectCsf b in
   let this = MultR (weakenR $\Gamma''$ a') b' in
	((n' + n'') ** (($\Gamma'$++$\Gamma''$) 
	  ** (convertVectInExprR (plusAssociative n n' n'')
	                   (vectAppendAssociative $\Gamma$ $\Gamma'$ $\Gamma''$) this)))
\end{lstlisting}
\end{center}
\caption{Automatic reflection - case of a multiplication}
\figrule
\end{figure}

@@

\end{lstlisting}
\end{center}
\caption{Automatic reflection - case of constants and variables}
\figrule
\end{figure}

We've omitted to show a few conversions of type in order to keep this part of the definition more readable. \\
\\
It is remarkable that the reflected term is guaranteed to be a faithful representation of the input. We've been able to define this function with a very strong and precise type because Idris has a $\%syntax$ command which let us do arbitrary pattern matching on syntax, and this $\%syntax$ produces functions which are typed, unlike Ltac terms in Coq.

>>>>

\section{The General Problem: A Hierarchy of Tactics}

\label{sect:general}

@@

All of our tactics will require to have a way of testing this equivalence between elements of the underlying set, that is to say, a way to test equivalence between constants. For this reason, we define a notion of ``set\footnote{This notion of ``Set" isn't a formalisation of sets and their elements, but is only the Setoid that we need} ", which only requires the definition of the equivalence relation --accompanied with the proofs that this is indeed an equivalence relation-- and this equivalence test $set\_eq$. All the algebraic structures will later extend this type class :

@@

    set_eq : (x:c) $\rightarrow$ (y:c) $\rightarrow$ Maybe (x $\simeq$ y)
\end{lstlisting}
\end{center}
\caption{Set}
\label{Set}
\figrule
\end{figure}
If the user wants to prove propositional equalities, then he will simply instantiate $(\simeq)$ with the built-in $(=)$ during the definition of the instance of $Set$.
Note that $(\simeq)$ is only weakly decidable in the sense that $set\_eq$ only produces a proof when the two elements are equivalent, but it doesn't produce a proof of dis-equivalence when they are different -- instead, it simply produces the value $Nothing$--. That's quite natural, since we want to generate proof of equivalence, and not to generate counter examples for proving dis-equivalence, which is another problem.

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
class Set c => Magma c where
    Plus : c $\rightarrow$ c $\rightarrow$ c
\end{lstlisting}
\end{center}
\caption{Magma}
\label{Magma}
\figrule
\end{figure}

This code means that a type $c$ (for $carrier$) is a Magma if it is already a Set (ie, it is equiped with the equivalence relation $\simeq$ and the test $set\_eq$), and if it has a $Plus$ operation.
In fact, all operations, like the Plus here, need to be "compatible" with the equality : $Plus\_preserves\_equiv : \{c1:c\} \rightarrow \{c2:c\} \rightarrow \{c1':c\} \rightarrow \{c2':c\} \rightarrow (c1 \simeq c1') \rightarrow (c2 \simeq c2') \rightarrow (Plus\ c1\ c2) \simeq (Plus\ c1'\ c2')$. This need only comes from the fact that we're dealing with any equivalence relation.

A bit more interesting is the Semi-Group typeclass. A Semi-Group is a Magma (ie, it still has a $Plus$ operation), but moreover it has the property of associativity for this operation.

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
class Magma c => SemiGroup c where
    Plus_assoc : (c1:c) $\rightarrow$ (c2:c) $\rightarrow$ (c3:c) 
               -> (Plus (Plus c1 c2) c3 $\simeq$ Plus c1 (Plus c2 c3))
\end{lstlisting}
\end{center}
\caption{Semi-Group}
\label{SemiGroup}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
class SemiGroup c => Monoid c where
    Zero : c    
    Plus_neutral_1 : (c1:c) $\rightarrow$ (Plus Zero c1 $\simeq$ c1)    
    Plus_neutral_2 : (c1:c) $\rightarrow$ (Plus c1 Zero $\simeq$ c1)
\end{lstlisting}
\end{center}
\caption{Monoid}
\label{Monoid}
\figrule
\end{figure}
We can continue the hierarchy with groups, which are a more interesting.
A group is a monoid, with two new operations. The binary operation $Minus$, and the unary operation $Neg$. We must have the property that $Minus$ can always be simplified with the $Neg$ and the $Plus$. That means that $Minus$ is not a "primitive" operation of a Group, since we can always rewrite $(a-b)$ into $(a\ +\ (-b))$. We let the possibility to express a $Minus$ just for convenience for the user, as he won't have to rewrite by hand his $Minus$ operations with sums of negations.
The second axiom, which is the most important one for a Group, is the fact that any value $c1$ admits $Neg\ c1$ for inverse, where being an inverse is the following property :

@@

class Monoid c => Group c where
    Minus : c $\rightarrow$ c $\rightarrow$ c
    Neg : c $\rightarrow$ c
    Minus_simpl : (c1:c) $\rightarrow$ (c2:c) $\rightarrow$ Minus c1 c2 $\simeq$ Plus c1 (Neg c2) 
    Plus_inverse : (c1:c) $\rightarrow$ hasSymmetric c _ c1 (Neg c1)
\end{lstlisting}
\end{center}
\caption{Group}
\label{Group}
\figrule
\end{figure}

@@

Note that the properties will either be obtained by implementation if the operations are real --computable-- functions, or by axioms if the user is working in an axiomatised theory where the operations ($Plus$, $Neg$, ...) are defined as axioms.

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
data ExprMa : Magma c $\rightarrow$ (Vect n c) $\rightarrow$ c $\rightarrow$ Type where
    ConstMa : (p : Magma c) $\rightarrow$ ($\Gamma$:Vect n c) $\rightarrow$ (c1:c)  $\rightarrow$ ExprMa p $\Gamma$ c1 
    PlusMa : {p : Magma c} $\rightarrow$ {$\Gamma$:Vect n c} $\rightarrow$ {c1:c} $\rightarrow$ {c2:c} 
         $\rightarrow$ ExprMa p $\Gamma$ c1 $\rightarrow$ ExprMa p $\Gamma$ c2 
         $\rightarrow$ ExprMa p $\Gamma$ (Plus c1 c2) 
    VarMa : (p:Magma c) $\rightarrow$ {$\Gamma$:Vect n c}
         $\rightarrow$ (i:Fin n) $\rightarrow$ ExprMa p $\Gamma$ (index i $\Gamma$)
\end{lstlisting}
\end{center}
\caption{Reflected terms for a Magma}
\label{ExprMa}
\figrule
\end{figure}

@@

Because there is no additional operations in a SemiGroup or in a Monoid, the datatypes for reflected terms in these two structures will have exactly the same shape as the one for Magma that we've given above.
However, the one for $Group$ will introduce two new constructors for the $Neg$ and $Minus$ operations :

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
data ExprG :  Group c $\rightarrow$ (Vect n c) $\rightarrow$ c $\rightarrow$ Type where
    ConstG : (p : Group c) $\rightarrow$ ($\Gamma$:Vect n c) 
         -> (c1:c) $\rightarrow$ ExprG p $\Gamma$ c1
    PlusG : {p : Group c} $\rightarrow$ {$\Gamma$:Vect n c} $\rightarrow$ {c1:c} $\rightarrow$ {c2:c} 
         $\rightarrow$ ExprG p $\Gamma$ c1 $\rightarrow$ ExprG p $\Gamma$ c2 
         $\rightarrow$ ExprG p $\Gamma$ (Plus c1 c2)
    MinusG : {p : Group c} $\rightarrow$ {$\Gamma$:Vect n c} $\rightarrow$ {c1:c} $\rightarrow$ {c2:c} 
         $\rightarrow$ ExprG p $\Gamma$ c1 $\rightarrow$ ExprG p $\Gamma$ c2 
         $\rightarrow$ ExprG p $\Gamma$ (Minus c1 c2)
    NegG : {p : Group c} $\rightarrow$ {$\Gamma$:Vect n c} $\rightarrow$ {c1:c} 
         $\rightarrow$ ExprG p $\Gamma$ c1 $\rightarrow$ ExprG p $\Gamma$ (Neg c1)
    VarG : (p : Group c) $\rightarrow$ {$\Gamma$:Vect n c} 
         $\rightarrow$ (i:Fin n) $\rightarrow$ ExprG p $\Gamma$ c1
\end{lstlisting}
\end{center}
\caption{Reflected terms in a Group}
\label{ExprG}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
groupReduce : {c:Type} $\rightarrow$ {n:Nat} $\rightarrow$ (p:Group c) $\rightarrow$ {$\Gamma$:Vect n c} 
	   $\rightarrow$ {x:c} $\rightarrow$ (ExprG p $\Gamma$ x) $\rightarrow$ (x' ** (ExprG p $\Gamma$ x', x $\simeq$ x'))
\end{lstlisting}
\end{center}
\caption{Type of the reduction function for terms reflecting elements in a Group}
\label{groupReduce}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
groupDecideEq : (p:Group c) $\rightarrow$ {$\Gamma$:Vect n c} $\rightarrow$ {x : c} $\rightarrow$ {y : c} 
	     $\rightarrow$ (ExprG p $\Gamma$ x) $\rightarrow$ (ExprG p $\Gamma$ y) 
	     $\rightarrow$ Maybe (x $\simeq$ y)
\end{lstlisting}
\end{center}
\caption{Type of the function for deciding equality between elements in a Group}
\label{groupDecideEqType}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
groupDecideEq p ex ey =
  let (x' ** (ex', px)) = groupReduce p ex in
  let (y' ** (ey', py)) = groupReduce p ey in
	     buildProofGroup p ex' ey' px py
\end{lstlisting}
\end{center}
\caption{Decides if two elements of a group are equal}
\label{groupDecideEq}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
buildProofGroup : (p:Group c) $\rightarrow$ {$\Gamma$:Vect n c} 
  $\rightarrow$ {x : c} $\rightarrow$ {y : c} $\rightarrow$ {x':c} $\rightarrow$ {y':c} 
  $\rightarrow$ (ExprG p $\Gamma$ x') $\rightarrow$ (ExprG p $\Gamma$ y') 
  $\rightarrow$ (x $\simeq$ x') $\rightarrow$ (y $\simeq$ y') 
  $\rightarrow$ (Maybe (x $\simeq$ y))
buildProofGroup p ex' ey' px py with (exprG_eq p ex' ey')
    buildProofGroup p ex' ex' px py | Just refl = ?MbuildProofGroup
    buildProofGroup p ex' ey' px py | Nothing = Nothing
\end{lstlisting}
\end{center}
\caption{Composes the two proofs if the normal forms are the same}
\label{buildProofGroup}
\figrule
\end{figure}
We've used here the function $exprG\_eq$ to decide the syntactical equality between the normalised reflected terms $ex'$ and $ey'$. This function plays the same role as $eqExpr$, presented on section 2.3 for the smaller example. Also, the proof for the metavariable $MbuildProofGroup$ corresponds exactly to what was done for the metariable $MbuildProof$ in the smaller example.

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
ConstantsRingReflector : {c:Type} $\rightarrow$ (p:Ring c) $\rightarrow$ Type
ConstantsRingReflector {c=c} p = 
     ({n:Nat} $\rightarrow$ ($\Gamma$:Vect n c) $\rightarrow$ (x:c) $\rightarrow$ Maybe (ExprR p $\Gamma$ x))
\end{lstlisting}
\end{center}
\caption{Type of the function doing the reflection for constants}
\label{ConstantsRingReflector}
\figrule
\end{figure}

@@

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
reflectRingTerm : {c:Type} $\rightarrow$ {p:Ring c} $\rightarrow$ {n:Nat} $\rightarrow$ ($\Gamma$ : Vect n c) 
     $\rightarrow$ (funReflectCsf:ConstantsRingReflector {c=c} p) $\rightarrow$ (x:c) 
     $\rightarrow$ (n' ** ($\Gamma'$:Vect n' c ** (ExprR {c=c} {n=n+n'} p ($\Gamma$ ++ $\Gamma'$) x)))
\end{lstlisting}
\end{center}
\caption{Automatic reflection to ring}
\label{reflectRingTermType}
\figrule
\end{figure}

This function will work very similarly to the reflection function for $Nat$ that we've writen in section~\ref{sect:ReflectNat}. Here, there are just more constructions to deal with, because $c$ is equipped with negations, subtractions and multiplications. We just show the pattern for the multiplication.

\begin{figure}[H]
\figrule
\begin{center}
\begin{lstlisting}
reflectRingTerm {p} {n=n} $\Gamma$ funReflectCsf (a*b) = 
   let (n' ** ($\Gamma'$ ** a')) = reflectRingTerm $\Gamma$ funReflectCsf a in
   let (n'' ** ($\Gamma''$ ** b')) = reflectRingTerm ($\Gamma$ ++ $\Gamma'$) funReflectCsf b in
   let this = MultR (weakenR $\Gamma''$ a') b' in
	((n' + n'') ** (($\Gamma'$++$\Gamma''$) 
	  ** (convertVectInExprR (plusAssociative n n' n'')
	                   (vectAppendAssociative $\Gamma$ $\Gamma'$ $\Gamma''$) this)))
\end{lstlisting}
\end{center}
\caption{Automatic reflection - case of a multiplication}
\label{reflectRingTerm_pattern1}
\figrule
\end{figure}

@@

\end{lstlisting}
\end{center}
\caption{Automatic reflection - case of constants and variables}
\label{reflectRingTerm_pattern2}
\figrule
\end{figure}

We've omitted to show a few conversions of type in order to keep this part of the definition more readable. \\
\\
It is remarkable that the reflected term is guaranteed to be a faithful representation of the input. We've been able to define this function with a very strong and precise type because Idris has a ``$\%syntax$" command which let us do arbitrary pattern matching on syntax, and the functions defined with ``$\%syntax$" are typed, unlike Ltac terms in Coq.
